Tunnels to Towers: Secure Virtual Private Networking for CCN

### 2017-01-07 paper/04-design.tex
Design updates
Paper: adding first draft of system and adv model section

@@

>>>>

\subsection{CCVPN Design}

@@

\subsection{System and Security Model}

Our security analysis considers the worst case scenario, in which the consumer issues an interest that has not been cached in any of the routers from the consumer nor producer domains. Therefore, the interest must traverse the whole network until reaching the content producer. Conversely, the content needs to be forwarded all the way back though the same path satifying the routers' PIT entries. A system that is secure in this worst case is also secure when the content has been previouly cached in some router along the way.

\textbf{Adversary Goals and Capabilities.} The goal of the adversary is to link a given encapsulated interest to the original interest issued by the consumer or a given encrypted content to the original content issued by the producer. An adversary is also consired succesful if it is able to impersonate the content produccer by faking a content response. Since the original interest and the original content are visible inside the consumer and producer domains, we here assume that the adversary cannot eavesdrop or compromise hosts inside such domains \footnote{In the case that communication should be anonomous even to nodes inside the consumer and producer domains, $G_c$ and $G_p$ could be ran as processes within the consumer and producer hosts, respectively. This way, packects exchanged between them would remain anonimous to any other node in the network}. This also means that, as components of the producer and consumer domains, we assume that the gateways $G_c$ and $G_p$ cannot be compromised.

In our model the adversary is allowed to perform the following actions (when outside the consumer and producer domains):

\begin{itemize}
	\item \textbf{Observe traffic replay and replace messages:}
	\item \textbf{Deploy compromised routers:}
	\item \textbf{Compromise existing routers:}
	\item \textbf{Deploy compromised caches:}
\end{itemize}

\subsection{Additional Considerations}

\textbf{Gateway-to-Gateway Authetication:}

\textbf{Denial of Service:}
